Are We Reusing Outdated and Licensed Code from Stack Overflow?

### 2017-02-18 cloneoverflow-latex/cloneoverflow.tex
(Section 2) fixed typos.

%\subsection{Experimental Setup}
\vspace{1ex}
To answer these four research questions, we perform an experiment to
locate and study the online code clones between Stack Overflow and open source
projects. The experimental framework is depicted in \Cref{fig:exp_framework}. 
We discuss the experimental setup below.

@@

We reply on two data sets in this study: Java code snippets on Stack Overflow and open source projects from the Qualitas corpus.

\subsubsection{Stack Overflow} we extracted Java code snippets from a snapshot of a Stack Overflow dump\footnote{https://archive.org/details/stackexchange} in January 2016. The archived dump has a size of 9 gigabytes. The data dump was in XML format containing information of \textbf{Posts} (questions and answers) and supporting data such as user accounts and timestamps of the posts. We were interested in code snippets embedded in posts which were located between {\small\texttt{<code></code>}} tags. A Stack Overflow thread contains a post of a question and several posts of answers where every answer has voting score from its users. An answer can also be marked as \textbf{accepted answer} by the questioner if the solution fixes his/her problem. We collected Java code snippets using two criteria. First, we were only interested in code snippets with at least six lines. Snippets that are smaller than six lines are usually spurious clones~\cite{Bellon2007}. Second, we only focused on code snippets in accepted answers. We chose the snippets in accepted answers because they actually solved the problems in the questions. Moreover, they are always displayed just below the questions which makes them more attractive to be reused than other answers. Each snippet was extracted from the dump and saved to a file. 
%using its post ID as the file's name. If an accepted answer had more than one code snippet, we appended an indexing number, starting from zero, after the post ID (e.g. 45051109\_0, and 45051109\_1.). Lastly, we added {\small\texttt{.java}} extension to the file's names so that clone detectors could recognise them. 
We obtained 144,064 Java code snippets which contain 2,347,269 lines of Java source code excluding comments and blank lines\footnote{Measured by cloc: https://github.com/AlDanial/cloc}.

>>>>

%\subsection{Experimental Setup}
\vspace{1ex}
To answer these four research questions, we perform an empirical study to
locate and study the online code clones between Stack Overflow and open source
projects. The experimental framework is depicted in \Cref{fig:exp_framework} and
we discuss our experimental setup below.

@@

We rely on two data sets in this study: Java code snippets on Stack Overflow and open source projects from the Qualitas corpus \cite{QualitasCorpus}.

\subsubsection{Stack Overflow} we extracted Java code snippets from a snapshot of a Stack Overflow dump\footnote{https://archive.org/details/stackexchange} in January 2016. The archived dump has a size of 9 gigabytes. The data dump was in XML format containing information of \textbf{Posts} (questions and answers) and supporting data such as user accounts and timestamps of the posts. We were interested in code snippets embedded in posts which were located between {\small\texttt{<code></code>}} tags. A Stack Overflow thread contains a post of a question and several posts of answers where every answer has voting score from its users. An answer can also be marked as \textbf{accepted answer} by the questioner if the solution fixes his/her problem. We collected Java code snippets using two criteria. First, we were only interested in code snippets with at least six lines. Snippets that are smaller than six lines are usually spurious clones~\cite{Bellon2007}. Second, we only focused on code snippets in accepted answers. We chose the snippets in accepted answers because they actually solved the problems in the questions. Moreover, they are always displayed just below the questions which makes them more attractive to be reused than other answers. Each snippet was extracted from the dump and saved to a file. 
%using its post ID as the file's name. If an accepted answer had more than one code snippet, we appended an indexing number, starting from zero, after the post ID (e.g. 45051109\_0, and 45051109\_1.). Lastly, we added {\small\texttt{.java}} extension to the file's names so that clone detectors could recognise them. 
We obtained 144,064 Java code snippets which contain 2,346,267 lines of Java source code excluding comments and blank lines\footnote{Measured by cloc: https://github.com/AlDanial/cloc}.
